\TitlePt

### 2016-03-19 thesis.tex
Add Latex converted text for fatiando paper
Fixed the figures and code samples. Still missing the references.
Add Tesseroids paper to thesis
Add Moho inversion paper to thesis
This will be changed a bit still as corrections from Valeria come in
Establish keywords for thesis
Rename papers with the actual subject, not just number
Needed to reorder the chapters so paper1, etc, didn't make much sense
anymore.
First draft of english abstract
Separated abstracts into a file.
Add valeria as first examiner

\documentclass[dsc]{on}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{enumerate} %para gerar listas numeradas
\usepackage{graphicx}  %para figuras eps

\makelosymbols
\makeloabbreviations

% Document metadata
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\TitleEn}{
    Title
}
\newcommand{\TitlePt}{
    Título
}
% Metadata for the generated PDF
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
    pdftitle={\TitleEn},
    pdfauthor={Leonardo Uieda (leouieda@gmail.com)},
    pdfsubject={},
    pdfkeywords={},
    pdfcreator={pdfTeX},
    allcolors=blue,
}

@@

\title{\TitlePt}
\foreigntitle{\TitleEn}
\author{Leonardo}{Uieda}
\advisor{Profa.}{Valérica Cristina Ferreira}{Barbosa}{D.Sc.}
\examiner{Prof.}{Nome do Primeiro Examinador Sobrenome}{D.Sc.}
\examiner{Prof.}{Nome da Segunda Examinadora Sobrenome}{Ph.D.}
\examiner{Dr.}{Nome da Terceira Examinadora Sobrenome}{D.Sc.}
\examiner{Prof.}{Nome do Quarto Examinador Sobrenome}{Ph.D.}
\examiner{Prof.}{Nome do Quinto Examinador Sobrenome}{Ph.D.}
\department{COGE}
\date{03}{2016}

\keyword{Primeira palavra-chave}
\keyword{Segunda palavra-chave}
\keyword{Terceira palavra-chave}

@@

\begin{abstract}

Apresenta-se, nesta tese, ...

\end{abstract}

\begin{foreignabstract}

In this work, we present ...

\end{foreignabstract}

\tableofcontents
\listoffigures
\listoftables
\printloabbreviations

@@

\include{introduction}
\include{paper1}
\include{paper2}
\include{paper3}
\include{conclusion}

>>>>

\documentclass[dsc]{on}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{url}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

% Document metadata
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\TitleEn}{
    Forward modeling and inversion of gravitational fields in spherical
    coordinates
}
\newcommand{\TitlePt}{
    Modelagem direta e inversão de campos gravitacionais em coordenadas
    esféricas
}
% Metadata for the generated PDF
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
    pdftitle={\TitleEn},
    pdfauthor={Leonardo Uieda (leouieda@gmail.com)},
    pdfsubject={},
    pdfkeywords={},
    pdfcreator={pdfTeX},
    allcolors=blue,
}

@@

\title{\TitlePt}
\foreigntitle{\TitleEn}
\author{Leonardo}{Uieda}
\advisor{Dra.}{Valérica Cristina Ferreira}{Barbosa}{D.Sc.}
\examiner{Dra.}{Valérica Cristina Ferreira Barbosa}{ON/MCTI}
\examiner{Prof.}{Nome da Segunda Examinadora Sobrenome}{Ph.D.}
\examiner{Dr.}{Nome da Terceira Examinadora Sobrenome}{D.Sc.}
\examiner{Prof.}{Nome do Quarto Examinador Sobrenome}{Ph.D.}
\examiner{Prof.}{Nome do Quinto Examinador Sobrenome}{Ph.D.}
\department{COGE}
\date{03}{2016}

\keyword{Gravimetria}
\keyword{Inversão}
\keyword{Software}

@@

\include{abstract}

\tableofcontents
\listoffigures
\listoftables

@@

\include{introduction}
\include{paper-tesseroids}
\include{paper-fatiando}
\include{paper-moho}
\include{conclusion}
